---
title: "Project 1"
author: "Maliat"
date: "2/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("C:/Users/malia/OneDrive/Desktop/MSDS DATA 607")
```

## R Markdown
```{r include=FALSE}
library(tidyverse)
library(stringr)
library(magrittr)
library(foreign)
library(descr)
library(lubridate)
library(rebus)
library(glue)
```


```{r}
Prac_chess_datasets<-read.delim("https://raw.githubusercontent.com/maliat-hossain/chess-data/main/tournamentinfo.txt",header = FALSE, sep = "|")
```

### In this project,  a text file is given with chess tournament results where the information has some structure. The objective  is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database)with the following information for all of the players:Player’s Name, Player’s State, Total Number of Points, Player’s Pre-Rating, and Average Pre Chess Rating of OpponentsFor the first player, the information would be:
### Gary Hua, ON, 6.0, 1794, 1605

### A new dataframe is created. Player number,player name ,player state,player points, player pre-rating was extracted by implementing string manipulation  from the given datasets.


```{r}

# 1. Loop over the dataset to get the Valid values and set information under variables. 
# 2. Create a new Dataframe and save those variables under different column. 
# 3. Calculte the ELO score of the opponent. 


refined_chess_datasets = NULL

for (i in 1:nrow(Prac_chess_datasets)){
  PlayerNumber<- suppressWarnings(as.numeric(Prac_chess_datasets$V1[i]))
  isValid <- grepl("[-]?[0-9]+[.]?[0-9]*|[-]?[0-9]+[L]?|[-]?[0-9]+[.]?[0-9]*[eE][0-9]+", PlayerNumber)

  if(isValid){
    PlayerName <- Prac_chess_datasets$V2[i]
    PlayerPoints <- Prac_chess_datasets$V3[i]
    PlayerState <- Prac_chess_datasets$V1[i+1]
    PlayerDetails <- Prac_chess_datasets$V2[i+1]
    PlayerRankSplit <- strsplit(PlayerDetails, split = "/")[[1]]
    PlayerRank <- PlayerRankSplit[[1]]
    PlayerRating <-PlayerRankSplit[[2]]
    
    PlayerRatingNew <- str_remove_all(PlayerRating, "[R:]")
    PlayerRatingSplit <- strsplit(PlayerRatingNew, split = "->")[[1]]
    PlayerPreRating <- PlayerRatingSplit[[1]]
   
   
    refined_chess_datasets = rbind(refined_chess_datasets, data.frame(PlayerNumber, PlayerName, PlayerState, PlayerPoints, PlayerPreRating))
    
  }
    
}


```

### Captured ratings of opponent for each round, and stored it in a new data frame. Measured the mean value from the new data frame. For this purpose string extract command was implemented.
```{r}

refined_chess_datasets_round = NULL

for (i in 1:nrow(Prac_chess_datasets)){
  PlayerNumber<- suppressWarnings(as.numeric(Prac_chess_datasets$V1[i]))
  isValid <- grepl("[-]?[0-9]+[.]?[0-9]*|[-]?[0-9]+[L]?|[-]?[0-9]+[.]?[0-9]*[eE][0-9]+", PlayerNumber)

  if(isValid){
    PlayerName <- Prac_chess_datasets$V2[i]
    
    Round1 <- as.numeric(str_extract(Prac_chess_datasets$V4[i], "[[:digit:]]+"))
    Round2 <- as.numeric(str_extract(Prac_chess_datasets$V5[i], "[[:digit:]]+"))
    Round3 <- as.numeric(str_extract(Prac_chess_datasets$V6[i], "[[:digit:]]+"))
    Round4 <- as.numeric(str_extract(Prac_chess_datasets$V7[i], "[[:digit:]]+"))
    Round5 <- as.numeric(str_extract(Prac_chess_datasets$V8[i], "[[:digit:]]+"))
    Round6 <- as.numeric(str_extract(Prac_chess_datasets$V9[i], "[[:digit:]]+"))
    Round7 <- as.numeric(str_extract(Prac_chess_datasets$V10[i], "[[:digit:]]+"))
    
    Round1OppPreRating <- as.numeric((sub("P.*", "\\1", refined_chess_datasets$PlayerPreRating[Round1])))
    Round2OppPreRating <- as.numeric((sub("P.*", "\\1", refined_chess_datasets$PlayerPreRating[Round2])))
    Round3OppPreRating <- as.numeric((sub("P.*", "\\1", refined_chess_datasets$PlayerPreRating[Round3])))
    Round4OppPreRating <- as.numeric((sub("P.*", "\\1", refined_chess_datasets$PlayerPreRating[Round4])))
    Round5OppPreRating <- as.numeric((sub("P.*", "\\1", refined_chess_datasets$PlayerPreRating[Round5])))
    Round6OppPreRating <- as.numeric((sub("P.*", "\\1", refined_chess_datasets$PlayerPreRating[Round6])))
    Round7OppPreRating <- as.numeric((sub("P.*", "\\1", refined_chess_datasets$PlayerPreRating[Round7])))
    
    MeanOppRating<- (mean(c(Round1OppPreRating, Round2OppPreRating, Round3OppPreRating, Round4OppPreRating, Round5OppPreRating, Round6OppPreRating, Round7OppPreRating), na.rm=TRUE))
    
    refined_chess_datasets_round = rbind(refined_chess_datasets_round, data.frame(PlayerNumber, PlayerName, Round1OppPreRating, Round2OppPreRating, Round3OppPreRating, Round4OppPreRating, Round5OppPreRating, Round6OppPreRating, Round7OppPreRating, MeanOppRating))
    
    
    
  }
  
}


```

```{r}
head(refined_chess_datasets_round)
```

### Created final data frame with all the required column. Also, exported data to a CSV file.

```{r}
# Add Average Opponents Rating to the Existing DataFrame. 

FinalChessData <- data.frame("PlayerNumber" = refined_chess_datasets$PlayerNumber, "PlayerName" =refined_chess_datasets$PlayerName, "State" = refined_chess_datasets$PlayerState, "Points" = refined_chess_datasets$PlayerPoints, "Pre-Rating" = refined_chess_datasets$PlayerPreRating, "OpponentsAvgRating"  = refined_chess_datasets_round$MeanOppRating)


head(FinalChessData)

write.csv(FinalChessData,"C:/Users/malia/OneDrive/Desktop/MSDS DATA 607/FinalChessData.csv", row.names = FALSE)


```




